\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{\articletitle}

### 2015-04-07 paper/paper.tex
paper updates

For this paper, the time complexity of the algorithms will be calculated. The difference in performance between the cases will be shown with a statistical analysis on computational results as well as the calculated time complexities.

@@

For every chosen test instance, the run times for both algorithms was determined. After all testing all instances had been completed, the results were compared and tested...
\\ \\
\textbf{\emph{TODO:} possibly rewrite the testing process after the testing; make sure timer details are correct; what statistical tests are we using?}

@@

To solve the graph isomorphism problem more efficiently, we use preprocessing algorithms which replaces twins and false twins by single precolored vertices such that:
\begin{compactenum}
\item Twins have the same color $\iff$ Twins have the same size (number of vertices).
\item False twins have the same color $\iff$ False twins have the same size (number of vertices).
\item A twin and a false twin can't have the same color.
\end{compactenum}
\subsection{Implementation}
The algorithm is divided into two subalgorithms. The subalgorithm \textit{gettwins} finds all twins and false twins and the subalgorithm \textit{preprocessing} replaces each (false) twin by a single colored vertex as described above. In the following subsections these algorithms and their worst case time complexities will be analyzed. The elementary operation is the comparison of two elements. In those subsections $n$ is the number of vertices of a graph $G(V,E)$ and $m$ is the number of edges of that graph.

@@

Results here \\
And statistical analysis of the results

@@

\end{document}
Status API Training Shop Blog About
© 2015 GitHub, Inc. Terms Privacy Security Contact

>>>>

For this paper, the time complexity of the algorithms will be calculated. The difference in performance between the cases will be shown by computational results as well as the calculated time complexities.

@@

For every chosen test instance, the run times for both algorithms was determined. After all testing all instances had been completed, the results were compared.
\\ \\
\textbf{\emph{TODO:} possibly rewrite the testing process after the testing; make sure timer details are correct}

@@

To solve the graph isomorphism problem more efficiently, we use preprocessing algorithms which replaces twins and false twins by single precolored vertices such that:
\begin{compactenum}
\item Twins have the same color $\iff$ Twins have the same size (number of vertices).
\item False twins have the same color $\iff$ False twins have the same size (number of vertices).
\item A twin and a false twin can't have the same color.
\end{compactenum}

\subsection{Implementation}
The algorithm is divided into two subalgorithms. The subalgorithm \textit{gettwins} finds all twins and false twins and the subalgorithm \textit{preprocessing} replaces each (false) twin by a single colored vertex as described above. In the following subsections these algorithms and their worst case time complexities will be analyzed. The elementary operation is the comparison of two elements. In those subsections $n$ is the number of vertices of a graph $G(V,E)$ and $m$ is the number of edges of that graph.

@@

Results here

@@

\end{document}
